\chapter{Summary}

	\hspace{15pt}The first milestone of the project has been reached successfully, our main goal was getting to know this very complicated system and design the plans of its advanced control software. The biggest challenge is implementing the mathematical model of a three-dimension coordinate system on this manipulator. Fortunately, Arduino IDE is one of the simplest and easily usable development tools.


	We think that our method is very effective with a very early constructed test for the software. This is not a pure example of TDD (Test Driven Development), but it has its own advantages too, and it is efficient enough for this project.


	We started to discover a very interesting and very popular field of robotics. Robot manipulators are the most common robots all over the world. They are used in ever modern factory. They have the oldest origins, but with Industry 4.0 they have developed rapidly, and they have many more opportunities in the future. Robot manipulators ca be integrated into other types of robotic system, for example on the board of a mobile robot, or a manipulator can be part of a co-robot system.


	\section{Future plans}
		
		\hspace{15pt}In the second part of the semester our goal will be to finish our planned work, implement the solution of the mathematical model, write the documentation, and specify system tests. Hopefully, after the execution of the tests we will report that everything is passed, and the robot manipulator will work safely.
		
		
	We have further plans for the system and for other semesters, the movements of the robotic arm might be logged by other Arduino add-on devices, and this log files could be used for developing the software of the arm.